Holomorphic field theories and higher algebra

### 2024-10-05 draft.tex
working on bib

There is a higher-dimensional analog of the chiral sector of the scalar field.
Let $X$ be a complex manifold of dimension $2n+1$, i.e., odd.
The fields are the $(n+1,n)$-forms $\alpha \in \Omega^{n+1,n}(X)$ that satisfy the constraint
\beqn
\del \alpha = 0.
\eeqn
(When $n=0$ and $X$ is simply a Riemann surface, 
this constraint is automatic.)
The action functional is $\int_X \alpha \dbar(\del^{-1} \alpha)$, the same as~\eqref{eqn:scalar1}.
Generally, this theory is the holomorphic part of a higher-form scalar theory, with action
\beqn
\int_X \|C\|^2 \op{dvol} = \int_X \d C \wedge \star \d C , 
\eeqn
where $C \in \Omega^{2n+1}(X)$.
For more details we refer to~\cite{GRWwzw}.

@@

Costello, inspired by the methods of Axelrod-Singer and Kontsevich,
found a framework for perturbative renormalization that works with a large class of elliptic complexes.
When applied to Dolbeault complexes arising in Kodaira-Spencer (or BCOV) theory, 
he and Li found some remarkable simplifications and good behavior \cite{??}.
In \cite{LiVertex} Li showed, by very clever analysis, that holomorphic field theories in complex dimension one (i.e., chiral conformal field theories) are finite to all orders in perturbation theory; 
this result was later extended to arbitrary Riemann surfaces in \cite{Jie and Si}.
Following up (cf. his thesis \cite{BWthesis} and its offshoot \cite{BWhol}), Williams laid a systematic mathematical foundations:
\begin{itemize}
\item he established key analytic results about holomorphic renormalization, 
showing that it is highly manageable, with no counterterms to 1-loop; and
\item characterized the one-loop anomalies  (i.e., obstructions to BV quantization).
\end{itemize}
These apply to all holomorphic theories on $\CC^n$,
but the techniques typically extend to more general complex manifolds.

In the last few years,
there has a been a buzz of recent activity on the renormalization of holomorphic field theories.
In work of Budzik, Gaiotto, Kulp, Wu, Yu, a strategy for proving UV finiteness for certain graphs (called Laman graphs) at arbitrary genus in a holomorphic quantum field theory is developed \cite{BGKWY}.
\owen{I think the term "UV finiteness" is too physics-y, and I don't find it very illuminating even then.}
\brian{I think it would be more confusing to use a different term. But you can explain how it's the issue of `overlapping supports' of distributions; that is, it's an issue about `local integrability'. In fact, in their work Axelrod and Singer already use the term ultraviolet.}
The key idea is to combine the heat kernel analysis with the sort of compactifications that are used in the theory of configuration spaces.

@@

In general, Eager's suggestion opens up a fascinating vein of inquiry:
\begin{quote}
how do physical results about supersymmetric gauge theories behave under twisting to holomorphic or topological theories?
\end{quote}
We have found, so far, that these results often admit clean mathematical formulations and that the holomorphic (or topological) twists involve constructions of natural interest in geometry and representation theory.
In \cite{EGW} we and Chris Elliott explored twists of $\cN=4$ supersymmetric Yang--Mills theory,
provided their quantizations, and began analyzing their factorization algebras.
One might can also ask about the twisted versions of S-duality and how to provide those conjectured equivalences.
The answer to this question has been studied by Surya Raghavendran and Philsang Yoo \cite{RYsduality} using Costello and Li's description of spacetime twists of superstring theories in terms of topological string theory \cite{CLsugra,CLtypeI}. 
A further localization of $S$-duality has also been studied by Costello and Gaiotto \cite{CGholography}.

\begin{rmk}
Our discussion here is ahistorical.
Witten initiated this vein of research for twists that are topological \cite{WittenTwist},
and Costello advocated holomorphic twists \cite{CostelloHol}.  
Costello and Li initiated the use of holomorphic twists to study dualities particularly in the setting of the topological B-model \cite{CLbcov1,CLbcov2,CLbcov3}, and further extended this to non-topological strings \cite{CLsugra}. 
Eager's suggestion was a natural variation on this theme but it (seems to) involve physical ideas and methods that have not (yet) played a large role in Costello's program.
These ideas are extensively used in the program of twisted holography, which is growing rapidly at the moment.
(The interested reader might track the papers that cite those we have mentioned.)
\end{rmk}

>>>>

There is a higher-dimensional analog of the chiral sector of the scalar field.
Let $X$ be a complex manifold of dimension $2n+1$, i.e., odd.
The fields are the $(n+1,n)$-forms $\alpha \in \Omega^{n+1,n}(X)$ that satisfy the constraint
\beqn
\del \alpha = 0.
\eeqn
(When $n=0$ and $X$ is simply a Riemann surface, 
this constraint is automatic.)
The action functional is $\int_X \alpha \dbar(\del^{-1} \alpha)$, the same as~\eqref{eqn:scalar1}.
Generally, this theory is the holomorphic part of a higher-form scalar theory, with action
\beqn
\int_X \|C\|^2 \op{dvol} = \int_X \d C \wedge \star \d C , 
\eeqn
where $C \in \Omega^{2n+1}(X)$.
For more details we refer to~\cite{GRW_WZW}.

@@

Costello, inspired by the methods of Axelrod-Singer and Kontsevich,
found a framework for perturbative renormalization that works with a large class of elliptic complexes.
When applied to Dolbeault complexes arising in Kodaira-Spencer (or BCOV) theory, 
he and Li found some remarkable simplifications and good behavior \cite{CLbcov}.
In \cite{LiVertex} Li showed, by clever analysis, that holomorphic field theories in complex dimension one (i.e., chiral conformal field theories) are finite to all orders in perturbation theory; 
this result was later extended to arbitrary Riemann surfaces in \cite{LiZhou}.
Following up (cf. his thesis \cite{BWthesis} and its offshoot \cite{Wrenorm}), Williams laid a systematic mathematical foundations:
\begin{itemize}
\item he established key analytic results about holomorphic renormalization, 
showing that it is highly manageable, with no counterterms to 1-loop; and
\item characterized the one-loop anomalies  (i.e., obstructions to BV quantization).
\end{itemize}
These apply to all holomorphic theories on~$\CC^n$,
but the techniques typically extend to more general complex manifolds.

In the last few years,
there has a been a buzz of recent activity on the renormalization of holomorphic field theories.
In work of Budzik, Gaiotto, Kulp, Wu, Yu, a strategy for proving UV finiteness for certain graphs (called Laman graphs) at arbitrary genus in a holomorphic quantum field theory is developed \cite{BGKWY}.
\owen{I think the term "UV finiteness" is too physics-y, and I don't find it very illuminating even then.}
\brian{I think it would be more confusing to use a different term. But you can explain how it's the issue of `overlapping supports' of distributions; that is, it's an issue about `local integrability'. In fact, in their work Axelrod and Singer already use the term ultraviolet.}
\owen{I agree that UV is a term many people use, but not among most of our target audience, which I view as algebraic geometers and higher algebra folks. Why not just say that we're showing no divergences appear and hence counterterms are not needed?}
The key idea is to combine the heat kernel analysis with the sort of compactifications that are used in the theory of configuration spaces.

@@

In general, Eager's suggestion opens up a fascinating vein of inquiry:
\begin{quote}
how do physical results about supersymmetric gauge theories behave under twisting to holomorphic or topological theories?
\end{quote}
We have found, so far, that these results often admit clean mathematical formulations and that the holomorphic (or topological) twists involve constructions of natural interest in geometry and representation theory.
In \cite{EGW} we and Chris Elliott explored twists of $\cN=4$ supersymmetric Yang--Mills theory,
provided their quantizations, and began analyzing their factorization algebras.
One might can also ask about the twisted versions of S-duality and how to provide those conjectured equivalences.
The answer to this question has been studied by Surya Raghavendran and Philsang Yoo \cite{RYsduality} using Costello and Li's description of spacetime twists of superstring theories in terms of topological string theory \cite{CLsugra,CLtypeI}. 
A further localization of $S$-duality has also been studied by Costello and Gaiotto~\cite{CGholography}.

\begin{rmk}
Our discussion here is ahistorical.
Witten initiated this vein of research for twists that are topological \cite{WittenTwist},
and Costello advocated holomorphic twists \cite{CosSUSY}.  
Costello and Li initiated the use of holomorphic twists to study dualities particularly in the setting of the topological B-model (see \cite{CLbcov} and follow ups), and further extended these ideas to non-topological strings \cite{CLsugra}. 
These ideas are extensively used in the program of twisted holography, which is growing rapidly at the moment.
(The interested reader might track the papers that cite those we have mentioned.)
Eager's suggestion was a natural variation on this theme but it (seems to) involve physical ideas and methods that have not (yet) played a large role in Costello's program.
\end{rmk}
